### 2016-06-30 store-consistency.tex
edits to sec. 5

>>>>

A distinguishing feature of our framework is that it is parameteric
over different isolation and consistency instantiations, whose
properties can be encapsulated within the trace invariant $\I$.  While
it is true that most relational databases implement standard ANSI SQL
isolation levels similar to the ones shown in
Fig.~\ref{fig:ansi-isolation}, there is no clear agreement on the
exact semantics of these isolation levels on various weakly-consistent
stores.  Thus, what Oracle calls serializable isolation is a slightly
stronger variant of snapshot isolation.  Having a parameterized
semantics and proof framework built on this semantics allows us to
support these variants without the need for semantics re-engineering
every time an application is retargeted to a new platform.  Moreover,
the need for high availability on geo-replicated stores is
incentivizing the development of new isolation levels. \emph{Parallel
  Snapshot Isolation}, for example, was proposed in 2011, and
\emph{Non-Monotonic Snapshot Isolation}~\cite{...} in 2013, both for
replicated stores. Commercial eventually-consistent stores have only
just started adopting transactions (the first release of Cassandra
with support for multi-key transactions is slated for later this
year), and all indications are that we should expect to see new
isolation instantiations in the future.

Without parameterization, we would need to carefully engineer a
reasoning framework for each isolation and consistency variant.
Clearly, each such framework would be incomparable to one another. On
the other hand, our treatment allows us to accommodate the myriad of
different isolation and store-consistency instances without the need
for bespoke specialization.
